Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-01 doc/tfp-2011/main.tex
*** empty log message ***

% TODO

>>>>

% motivation is finer control over task/workers/execution
% example 1: remove *some* tasks when others are completed
% example 2: interactive program (GUI, control, etc.)

The function \of{compute} above can actually be implemented in terms
of low-level primitives, such as adding a task, adding a worker,
performing one step of communication between master and workers, etc.
These primitives are provided in our API, such that the user can have
finer control over the execution of the distributed computation.
A type for distributed computations is introduced.
\begin{ocaml}
  type ('a, 'c) computation
\end{ocaml}
A computation is created with a function \of{create}, which accepts
the same \of{worker} and \of{master} as \of{compute}:
\begin{ocaml}
  val create : 
    worker:('a -> 'b) -> 
    master:('a * 'c -> 'b -> ('a * 'c) list) -> ('a, 'c) computation
\end{ocaml}
Contrary to \of{compute}, it takes no list of tasks and returns
immediately. Tasks can be added later using the following function:
\begin{ocaml}
  val add_task : ('a, 'c) computation -> 'a * 'c -> unit
\end{ocaml}
A function is provided to perform \emph{one step} of a given
computation:
\begin{ocaml}
  val one_step : ('a, 'c) computation -> unit
\end{ocaml}
Calling this function results in one exchange of messages between
master and workers: task assignments to workers, results returned to
the master, etc. A few other functions are provided, such as
\of{status} to query the status of a computation, \of{clear} to remove
all tasks, etc.

Using these low-level primitives, it is straightforward to implement
the \of{compute} function. Basically, it is as simple as the following:
\begin{ocaml}
let compute ~worker ~master tasks =
  let c = create worker master in
  List.iter (add_task c) tasks;
  while status c = Running do one_step c done
\end{ocaml}
